Extra Large Sequence Transformer Model for Chinese Word Segment

### 2021-01-16 A-BasicCommom/ACL2021/acl_law_examination.tex
1.acl2021 CN word segment.

\subsection{Segment Extraction}
The document of the court sentence usually states the arguing point of the two entities.
In this paper, a dictionary based arguing reason extractor was designed.
A total of 123 arguing reasons were classified by the legal experts out of 70 million
civil documents collected from the Chinese Court Sentence website.

Then I use several rule-based filters to extract meaningful segments.
As Figure-1 shows, the document has been split into several paragraphs,
the paragraph with important words are kept and other paragraphs are discarded.

\subsection{Extractive Sentence Summarization}

For the sentence importance scoring model, the experts wrote the summarization for each legal document.
Base on the written summarization, each sentence importance can be easily computed by checking the overlap words.
I use the pre-trained Chinese language model, which has multiple layers of transformers,
for encoding sentences.
As Figure-2 shows, the model layers are organized as follows:
Take the last two layers of the RoBERTa encoding, then do the concatenation and take the Maximum element from the character
sequence as representation for each sentence, then concatenating to a dropout layer, a softmax layer,
and the output layer.

The learning rate is $10^{-4}$, the max sequence length is 50, the dropout rate is 5\%, and the batch size is 1.
The epoch number is 3.
The experiment was carried on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of the high speed of memory each,
which can provide 420 tera-flops of computation capability.

The classification dataset is unbalanced, thus I copy the positive samples multiple times to balance the dataset.
In total, there are 782,895 samples for training and 42 samples for test in the Legal Sentence Importance dataset.
The test accuracy is 92.06\%.

>>>>

\subsection{Legal Question Answering Dataset}

I use a dataset collected by Zhong \etal, which contains 7775 knowledge-based QA pairs and 13297 case-analysis QA pairs.
Some questions have multiple options correct in the answer, while some have single option correct.

\subsection{Context Representation}

There are three descriptive information, namely question, options, and paragraphs for each item in the dataset.
The paragraph is optional for the knowledge based QA-pair and mandatory for the case analysis QA-pair.
The paragraph and the question always come together in a single paragraph.
There are always four options, and the correct options are not variant according to the question.

I use the BERT model as the representation for the question and option encoding.
In total, seven different BERT pre-trained language model were compared.
Google BERT for Chinese, Roberta BERT for Chinese, Roberta BERT 3 layers for Chinese,
Roberta BERT 3 layers for Chinese(1024 dim), Roberta BERT 24 layers for Chinese (1024 dim),
Extra Roberta BERT 24 layers for Chinese (1024 dim), Extra More Steps Roberta BERT 24 layers for Chinese (1024 dim).

### 2021-01-16 A-BasicCommom/ACL2021/acl_word_segment.tex
1.acl2021 CN word segment.

After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
To encode by XLNet, the mask tokens and the segment tokens are prepared.
The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
The padding tokens' make tokens are set to [0], and the segment tokens are set to [1] for telling the model the boundary of the sentences.
For encoding the sequence, all the layers are preserved for later usage.

@@

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryModel.pdf}}
\end{center}
   \caption{Different architectures for multi-grained summarization.
   (a) Extractive Sentence Summarization,
   (b) Sequence To Sequence Summarization.}
\label{fig:short}
\end{figure*}

>>>>

After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
To encode by XLNet and BERT model, the mask tokens and the segment tokens are prepared.
The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
The padding tokens' make tokens are set to [0], and the segment tokens are set to [1] for telling the model the boundary of the sentences.
For encoding the sequence, all the layers are preserved for later usage.
The vocabulary encoding used by LSTM word embedding doesn't need the mask tokens and segment tokens, the vocabulary was formed by characters extracted from the MSR2005 training dataset, its conversion from character set to half character encoding set,
and one padding token [PAD], and one unknown token [UNK]. There are 5245 tokens in the vocabulary, and the embedding size is 256.

@@

\subsection{Summary}

As Figure (1) shows, the Chinese word segment architecture are formed by input layer, encoder layer, concatenating layer, representation layer, CRF layer, and output layer.
In this paper, I mainly focus on discussing the improvement on the encoder layer
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{cws-architecture.pdf}}
\end{center}
   \caption{The Network Architecture for the Chinese word segment task.}
\label{fig:short}
\end{figure*}
